\section{Motivation} It could be interesting to create a mobile application combined with theoretical knowledge on mobile systems and methods for engineering mobile systems. Based on the CykelScore concept our focus will be on increasing the safety of biking by using mobile sensing to coordinate “Biking Buses” for younger kids supervised by older kids.   \\

\noindent
 In this solution we will have focus on designing a flexible architecture. Using known software design principle from \cite{Bass} and \cite{Baerbak10}, we discuss and reflect on different solutions.
 
 
 %**************************************Definition Software engineering
\begin{defi}[\textbf{Software engineering}]
Concerned with developing and maintaining software systems that behave reliably and efficiently, are affordable to develop and maintain,
and satisfy all the requirements that customers have defined for them. [ACM]
\end{defi}
%**************************************Definition Software engineering End


 %**************************************Definition Mobile systems
\begin{defi}[\textbf{Mobile systems}]
Mobile systems covers software systems that run on computers that are expected to be transported during normal usage. Systems depend on innovations in mobile
communications and mobile hardware.
\end{defi}
%**************************************Definition Mobile systems End


 %**************************************Definition Mobile systems
\begin{defi}[\textbf{Mobile sensing}]
Mobile sensing is the use of mobile devices for sensing and learning physical and social phenomenon and using such information for
informing, sharing and persuasion among humans.
\end{defi}
%**************************************Definition Mobile systems End


