% Admir
\section{Objectives}
\textcolor{red}{Problem and Objective: What is the (exact) problem to be addressed/solved with the application you build. Note, describe the problem and the overall objective only.}\\


\iffalse
\noindent
What we should address:
\begin{enumerate}
    \item  Analyze architectural structures and qualities of a mobile system and provide arguments for what needs to be done to evolve the architecture according to new and changing requirements
            
    \item  Explain the code base in a larger mobile system and explain how incremental expansions of functionality can be made according to changing requirements
    
    \item   Provide arguments for the choice of technologies in a given mobile system project taking into account the architectural and project requirements
    
    \item Provide arguments for how to architect mobile system solutions that address energy efficiency and resource availability challenges. 
\end{enumerate}
\fi

This project consists of two main parts. The first a theoretical background where we study the concepts behind mobile sensing. In the second part, we will describe our process for designing the bikingbus mobile application. Basically this project have the following objectives. 

\begin{enumerate}
    \item   Describe the theory behind different aspect of mobile sensing. The aim is to understanding the concept behind a mobile sensing application and what one needs to handle. 
            
    \item  Analyze requirements, design and prototype a mobile bikebus application with focus on the architectural design. From the requirements we shall address energy efficiency and resource availability. Known software design principles will be used to acquire high flexibility software quality to assist incremental changes in the demands. 

\end{enumerate}


