% Admir
\subsection{Report outline} 
The following section explains where to find what. The report consists of four chunks as seen in the below list. 

\begin{enumerate}
    \item Theoretical for Mobile Sensing
    \begin{enumerate}
        \item Mobile Sensing
        \item Sensor Challenges
    \end{enumerate}
    \item Design of application
    \begin{enumerate}
        \item Architectural qualities and tactics
        \item Solution Approach
    \end{enumerate}
    \item Implementation of application
    \begin{enumerate}
        \item Solution Description
    \end{enumerate}
    \item Reflection, Discussion and conclusion
\end{enumerate}

The first chunk "Theoretical for Mobile Sensing" contains information about what mobile sensing is and what kind of challenges accompany it, furthermore the BikeBus application is mentioned and how BikeBus tackles mobile sensing in different aspects. 

The second chunk "Design of application" focuses on the architecture of BikeBus. Different Quality Attribute Scenarios (QAS) are mentioned and tactics to solve the QAS'. The architecture description spans from interfaces and listeners used to the type of material design used for the application.

The third chunk "Implementation of application" explains the implementation of BikeBus. The focus is on non-trivial implementation, focusing on topics such as compression, distance calculations, activity recognition, location, several Google services and the data layer. Code is omitted in most cases as the report is accompanied by a zip file which contains the source code. 

The last chunk "Reflection, Discussion and Conclusion" contains topics such as the prioritization of BikeBus, the current solution, several challenges, perspective to other similar applications and a future works chapter explaining what would be nice to further add to BikeBus.   



The chunks should be read in chronological order as there are cross references from section to section. Figures that are determined to be too small have a higher resolution version in \ref{app:appendix} Appendix, which are referenced to in their appropriate sections. 

Several definitions are added to the report, this is to simply show which definitions the writers used for understanding certain topics, and to create common understanding of certain topics. 